\documentclass{mcmthesis}

\mcmsetup{
  tstyle=\color{black}\bfseries,
  tcn = 2602828,
  problem = F,
  sheet = true,
  titleinsheet = true,
  keywordsinsheet = true,
  titlepage = false,
  abstract = true
}

% ========== Package Configuration ==========
\usepackage{float}
\usepackage{placeins}  % for \FloatBarrier
\usepackage{needspace} % for avoiding orphan section titles
\usepackage{pifont}    % for \ding symbols
\usepackage{txfonts}
\usepackage{makecell}  % for multi-line table headers
\usepackage{threeparttable} % for table footnotes
\usepackage[font=small,labelfont=bf,justification=centering]{caption} % unified caption style

% ========== Safe Symbols ==========
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{array}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}

% ========== Page Layout Optimization ==========
\setlength{\parskip}{0.15em}
\setlist{nosep, leftmargin=1.5em}
\setlength{\floatsep}{5pt plus 2pt minus 2pt}
\setlength{\textfloatsep}{6pt plus 2pt minus 2pt}
\setlength{\intextsep}{5pt plus 2pt minus 2pt}
\setlength{\abovecaptionskip}{3pt}
\setlength{\belowcaptionskip}{1pt}
\setlength{\abovedisplayskip}{5pt}
\setlength{\belowdisplayskip}{5pt}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.70}
\renewcommand{\textfraction}{0.10}
\renewcommand{\floatpagefraction}{0.80}

% ========== References Formatting ==========
% Fix 1: URL line breaking - allow breaks at more characters
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother

% Fix 2: Hide hyperlink borders (print-friendly)
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  hidelinks
}

% Fix 3: Fixed-width reference numbers - ensures [1] to [99] align
\makeatletter
\renewcommand{\@biblabel}[1]{[#1]\hfill}
\renewenvironment{thebibliography}[1]
  {\section*{\refname}%
   \addcontentsline{toc}{section}{\refname}%
   \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
   \list{\@biblabel{\@arabic\c@enumiv}}%
        {\settowidth\labelwidth{\@biblabel{#1}}%
         \leftmargin\labelwidth
         \advance\leftmargin\labelsep
         \@openbib@code
         \usecounter{enumiv}%
         \let\p@enumiv\@empty
         \renewcommand\theenumiv{\@arabic\c@enumiv}}%
   \sloppy
   \clubpenalty4000
   \@clubpenalty \clubpenalty
   \widowpenalty4000%
   \sfcode`\.\@m}
  {\def\@noitemerr
    {\@latex@warning{Empty `thebibliography' environment}}%
   \endlist}
\makeatother

\graphicspath{{figures/}}

% ========== Custom Commands ==========
\newcommand{\modelname}{TECM}
\newcommand{\fullmodelname}{Task--Exposure--Congestion--Market}
\newcommand{\highlight}[1]{\textbf{#1}}
\newcommand{\insight}[1]{\noindent\textit{\textbf{Key Insight:} #1}}

% ========== Title ==========
\title{The Tipping Point Paradox: When AI Augmentation Becomes Displacement\\
\large A Task-Granular Framework for Career Evolution and Educational Adaptation}
\date{}

\begin{document}

% ===== Summary Sheet =====
\begin{abstract}
\textbf{Problem.} Educational institutions face unprecedented uncertainty: Generative AI technologies designed for human augmentation may, beyond critical adoption thresholds, precipitate employment displacement. We develop a principled framework to identify these thresholds and inform enrollment and curriculum decisions.

\textbf{Data.} We integrate three authoritative sources: O*NET 28.3 for task-level AI exposure ($K = 41$ work activities per occupation), BLS OEWS (2010--2024) for employment dynamics, and IPEDS (2015--2023) for educational supply. Structural parameters are calibrated against 12 years of pre-GenAI data (2010--2022, MAPE $<7\%$); GenAI-specific parameters are treated as scenario assumptions subject to sensitivity analysis.

\textbf{Model.} The Task--Exposure--Congestion--Market (TECM) framework comprises three coupled models: Model I (Task Decomposition) yields a Composite Exposure Index ($\Xi_o$) and Physical Protection Index ($P_i$); Model II (Verification-Bottleneck Congestion) generates occupation-specific tipping points $A^* = 1/(2s)$ where employment transitions from augmentation to displacement; Model III (Educational Feedback) demonstrates how curriculum interventions shift $A^*$ rightward by elevating workforce capability $V_s$.

\textbf{Results.} Application to three archetypal occupations reveals divergent trajectories: Information Security Analysts occupy a permanent augmentation basin ($A^* > 150\%$, employment $+15.8\%$ at $t=60$); Electricians exhibit robust physical protection ($P_i = 0.78$, adoption $<10\%$); Graphic Designers approach the displacement threshold ($A^* = 90.9\%$ vs.\ $A_{\text{cap}} = 85\%$). PRCC analysis identifies $A_{\text{cap}}$ (0.95), sub\_ratio ($-0.82$), and $\kappa_A$ (0.82) as highest-sensitivity parameters.

\textbf{Recommendations.} Carnegie Mellon (maintain enrollment; integrate frontier AI security tools); Lansing Community College (expand 9--13\%; emphasize physical task complementarity); Rhode Island School of Design (maintain enrollment; target curriculum AI-intensity $\phi = 0.25$ to shift $A^*$ beyond $A_{\text{cap}}$). The tipping point is not destiny---it is a design parameter amenable to institutional intervention.

\textbf{Critical Insight.} Occupational displacement is not predetermined by AI exposure alone; it emerges from the interaction between adoption rate, verification bottleneck saturation, workforce capability, and curriculum design. Educational institutions possessing actionable early-warning metrics (monitoring $A(t)$ relative to $A^*$, tracking substitution ratio $s(t)$, benchmarking graduate capability $V_s$) can proactively shift institutional strategy before critical thresholds are crossed. This framework transitions AI-employment analysis from fatalism (``jobs will be automated'') to agency (``we can shape outcomes through deliberate educational and institutional choices'').
\end{abstract}

\begin{keywords}
Task Decomposition; Verification Congestion; Tipping Point; Physical Protection; Educational Intervention; Gen-AI Adoption
\end{keywords}

\maketitle

\input{sections/1_introduction}
\input{sections/2_problem_analysis}
\input{sections/3_assumptions}
\input{sections/4_data_sources}
\input{sections/5_model_development}
\input{sections/6_results}
\input{sections/7_recommendations}
\input{sections/8_beyond_employment}
\input{sections/9_sensitivity}
\input{sections/10_strengths_limitations}
\input{sections/11_conclusion}
\input{sections/12_references}
\input{sections/14_appendix_data}
\input{sections/13_ai_report}

\end{document}
