% ========== Appendix A: Data Audit Trail ==========
\appendix
\section{Data Audit Trail}

This appendix documents the provenance of all empirical quantities used in model calibration and validation, ensuring full reproducibility and transparency.

\subsection{BLS OEWS Employment Data}

\begin{table}[H]
\centering
\caption{BLS OEWS Employment Time Series}
\label{tab:audit_bls}
\small
\begin{tabular}{lccc}
\toprule
\textbf{Year} & \textbf{ISA (15-1212)} & \textbf{Elec (47-2111)} & \textbf{GD (27-1024)} \\
\midrule
2010 & --- & 514,760 & 192,240 \\
2011 & --- & 512,290 & 191,550 \\
2012 & 72,670 & 519,850 & 191,440 \\
2013 & 78,020 & 542,680 & 194,360 \\
2014 & 80,180 & 566,930 & 197,540 \\
2015 & 88,880 & 592,230 & 204,850 \\
2016 & 96,870 & 607,120 & 210,710 \\
2017 & 105,250 & 631,080 & 217,170 \\
2018 & 108,060 & 655,840 & 217,810 \\
2019 & 125,570 & 688,620 & 215,930 \\
2020 & 138,000 & 656,510 & 201,440 \\
2021 & 157,220 & 650,580 & 204,040 \\
2022 & 163,690 & 690,050 & 211,890 \\
2023 & 175,350 & 712,580 & 212,720 \\
2024 & 187,940 & 773,950 & 223,240 \\
\bottomrule
\end{tabular}
\end{table}

\noindent\textbf{Source}: Bureau of Labor Statistics, Occupational Employment and Wage Statistics (OEWS), National May estimates.\\
\textbf{Access}: \url{https://www.bls.gov/oes/tables.htm}\\
\textbf{Extraction date}: January 2025\\
\textbf{Local file}: \texttt{data/external/processed/oews\_target\_soc\_2010\_2024.csv}\\
\textbf{Notes}: SOC 15-1212 (Information Security Analysts) introduced in SOC-2010 revision; consistent series available from 2012. Employment figures represent total national employment (``tot\_emp'' field).

\subsection{IPEDS Completions Data}

\begin{table}[H]
\centering
\caption{IPEDS Program Completions by Institution and Year}
\label{tab:audit_ipeds}
\small
\begin{tabular}{llcccccc}
\toprule
\textbf{Institution} & \textbf{CIP} & \textbf{Award} & \textbf{2019} & \textbf{2020} & \textbf{2021} & \textbf{2022} & \textbf{2023} \\
\midrule
CMU (211440) & 11.1003 & 7 & 84 & 92 & 79 & 70 & 143 \\
Lansing CC (170657) & 46.0302 & 2+3+21 & 26 & 28 & 16 & 17 & 32 \\
RISD (217493) & 50.0409 & 5+7 & 74 & 61 & 61 & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

\noindent\textbf{Source}: Integrated Postsecondary Education Data System (IPEDS), Completions Survey.\\
\textbf{Access}: \url{https://nces.ed.gov/ipeds/datacenter/}\\
\textbf{Extraction date}: January 2025\\
\textbf{Local file}: \texttt{data/external/processed/ipeds\_completions\_real\_targets\_2015\_2023.csv}\\
\textbf{Award level codes}: 1=Certificate $<$1yr, 2=Certificate 1--2yr, 3=Associate, 5=Bachelor's, 7=Master's, 17=Doctor's, 21=Post-baccalaureate certificate.\\
\textbf{Notes}: RISD (UnitID 217493) data for CIP 50.0409 unavailable in 2022--2023 IPEDS public release at time of extraction. Lansing CC totals aggregate across certificate and associate awards appropriate to electrician training programs.

\subsection{Institution Identification}

\begin{table}[H]
\centering
\caption{IPEDS Institution Identifiers}
\label{tab:audit_unitid}
\small
\begin{tabular}{llll}
\toprule
\textbf{Institution} & \textbf{UnitID} & \textbf{City, State} & \textbf{Verification} \\
\midrule
Carnegie Mellon University & 211440 & Pittsburgh, PA & IPEDS lookup confirmed \\
Lansing Community College & 170657 & Lansing, MI & IPEDS lookup confirmed \\
Rhode Island School of Design & 217493 & Providence, RI & IPEDS lookup confirmed \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Deleted/Corrected Claims}

The following claims from earlier drafts were removed or corrected due to insufficient sourcing:

\begin{itemize}[noitemsep]
\item ``1,416 unfilled electrician positions'' --- No verifiable BLS source identified; claim removed.
\item ISA E(2010) = 67,100 --- SOC 15-1212 series begins 2012; corrected to use 2012 value.
\item GD employment decline narrative --- Actual BLS data shows modest growth (192,240 $\to$ 223,240); narrative corrected.
\item IPEDS completions (CMU=287, Lansing=156, RISD=312) --- Values did not match IPEDS records; corrected to verified values.
\end{itemize}

\subsection{Model Parameters: Epistemic Classification}

\begin{table}[H]
\centering
\caption{Parameter Epistemic Status}
\label{tab:audit_params}
\small
\begin{tabular}{p{2.5cm}p{2cm}p{2.5cm}p{4.5cm}}
\toprule
\textbf{Parameter} & \textbf{Status} & \textbf{Calibration Target} & \textbf{Sensitivity Range} \\
\midrule
$\kappa_E$ & Calibrated & E(t) 2010--22 & Fixed post-calibration \\
$\delta_0$ & Calibrated & E(t) 2010--22 & Fixed post-calibration \\
$\varepsilon_D$ & Calibrated & E(t) 2010--22 & $\pm 40\%$ tested \\
$A_{\text{cap}}$ & Assumed & --- & $\pm 20\%$ tested \\
$\kappa_A$ & Assumed & --- & $[1.0, 2.5]\times$ baseline \\
$s_{\text{base}}$ & Assumed & --- & $\pm 30\%$ tested \\
$\theta_V$ & Assumed & --- & $\pm 30\%$ tested \\
$P_i$ & Derived & O*NET Work Context & Not varied \\
$\Xi_o$ & Derived & O*NET Work Activities & Not varied \\
\bottomrule
\end{tabular}
\end{table}

\noindent\textit{Calibrated}: Parameters fitted to 2010--2022 BLS employment data.\\
\textit{Assumed}: Parameters set via expert judgment or survey data; tested via sensitivity analysis.\\
\textit{Derived}: Parameters computed deterministically from O*NET task decomposition.
